---
title: "Preprocessing Experiment 4 data"
author: "Bodo Winter & Greg Woodin"
date: "05/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of Experiment 4

This is the analysis of Experiment 4. Start loading packages, function file and data:

```{r libraries, message = FALSE}

library(tidyverse)    # for data processing
library(stringr)    # for data processing
library(lme4)   # for mixed models
library(afex)   # for mixed models
library(lsr)   # for Cramer's V

source('../scripts/functions.R')

df <- read_csv("../data/E4_processed.csv")
df %>% print(n = 6, width = Inf)

```

Check how many subjects, how many male and female:

```{r sub_stats}

# Number of subjects:

length(unique(df$ID))

# Male/female:

apply(table(df$ID, df$Gender), MARGIN = 1,
      FUN = function(x) ifelse(x[1] > 0, 'Female', 'Male')) %>% table()

# Handedness:

hv <- c('left', 'ambi', 'right')
apply(table(df$ID, df$Handedness), MARGIN = 1,
      FUN = function(x) hv[which.max(x)]) %>% table()
```

Compute x- and y-axis ranges (across the four clicks). This is a rough indicator of axis use. We do this separately for each subject and each task (time, valence etc.)

```{r avg_range}

df_range <- df %>%
  group_by(ID, Type, Axis) %>%
  summarize(Min = min(Pixel),
            Max = max(Pixel)) %>%
  mutate(Range = Max - Min)
```

## Analysis of axis use via range (continuous)

First, let's explore some descriptive stats:

```{r range_avgs}

df_range %>% group_by(Type, Axis) %>%
	summarize(RangeM = mean(Range),
	RangeSD = sd(Range))
```

Make factors for ordering in plot:

```{r order_facs}

df_range <- df_range %>%
  ungroup %>%
  mutate(Type = factor(Type, levels = c('T', 'Q', 'N', 'V')))
```

Make a public-ready boxplot:

```{r get_boxplot_data}

x_box <- boxplot(Range ~ Type,
                 data = filter(df_range, Axis == 'x'),
                 plot = FALSE)
y_box <- boxplot(Range ~ Type,
                 data = filter(df_range, Axis == 'y'),
                 plot = FALSE)
```

Set columns (both quantity and number will be red):

```{r set_cols}
mycols <- c('steelblue4',
            'indianred4', 'indianred4', 'goldenrod3')
```

```{r range_plot, fig.width = 12, fig.height = 5}

xfac <- 0.1

quartz('', 12, 4)
par(mai = c(0.75, 1.5, 0.5, 0.5))
emptyplot(xlim = c(0, 10), ylim = c(0, 700))
axis(side = 2, at = seq(0, 700, 100),
	font = 2, las = 2, cex.axis = 1.35, lwd = 2)
mtext(text = 'Range (pixels)', side = 2, line = 3.8,
	font = 2, cex = 1.75)
axis(side = 1, at = seq(0.5, 3.5, 1),
	labels = c('Time', 'Quantity', 'Number', 'Valence'),
	font = 2, cex.axis = 1, line = -1.5, tick = FALSE)
axis(side = 1, at = c(2, 7),
	labels = c('x-axis', 'y-axis'),
	font = 2, cex.axis = 1.5, line = 0.5, tick = FALSE)
for (i in 1:4) {
	rect(xleft = i - 1 + xfac, xright = i - xfac,
		ybottom = x_box$stats[2, i],
		ytop = x_box$stats[4, i],
		col = mycols[i])
	segments(x0 = i - 1 + xfac + 0.05, x1 = i - xfac - 0.05,
		y0 = x_box$stats[3, i], lwd = 2)
	segments(x0 = seq(0.5, 3.5, 1)[i],
		y0 = x_box$stats[4, i],
		y1 = x_box$stats[5, i])
	segments(x0 = seq(0.5, 3.5, 1)[i],
		y1 = x_box$stats[2, i],
		y0 = x_box$stats[1, i])
	}
axis(side = 1, at = seq(0.5, 3.5, 1) + 5,
	labels = c('Time', 'Quantity', 'Number', 'Valence'),
	font = 2, cex.axis = 1, line = -1.5, tick = FALSE)
for (i in 1:4) {
	rect(xleft = i - 1 + xfac + 5, xright = i - xfac + 5,
		ybottom = y_box$stats[2, i],
		ytop = y_box$stats[4, i],
		col = mycols[i])
	segments(x0 = i - 1 + xfac + 0.05 + 5, x1 = i - xfac - 0.05 + 5,
		y0 = y_box$stats[3, i], lwd = 2)		
	segments(x0 = seq(0.5, 3.5, 1)[i] + 5,
		y0 = y_box$stats[4, i],
		y1 = y_box$stats[5, i])
	segments(x0 = seq(0.5, 3.5, 1)[i] + 5,
		y1 = y_box$stats[2, i],
		y0 = y_box$stats[1, i])
}
```

Models of this, with the afex package for likelihood ratio tests:

```{r afex_LRT, message = FALSE}
x_mdl <- mixed(Range ~ Type + (1|ID),
	data = filter(df_range, Axis == 'x'), method = 'LRT', check_contrasts = FALSE)
y_mdl <- mixed(Range ~ Type + (1|ID),
	data = filter(df_range, Axis == 'y'), method = 'LRT', check_contrasts = FALSE)
all_mdl <- mixed(Range ~ Type * Axis +
                   (1 + Axis|ID),
	data = df_range, method = 'LRT')
```

Check the likelihood ratio tests results:

```{r afex_results}
x_mdl
y_mdl
all_mdl
```

Check the individual models:

```{r check_models}
summary(x_mdl$full_model)
summary(y_mdl$full_model)
```

Check the full model:

```{r main_mdl_investigate}
summary(all_mdl$full_model)$coefficients
```

Sum-coding makes this quite difficult to interpret. Let's use a treatment-coded model:

```{r treatment_codes}
xmdl <- lmer(Range ~ Type * Axis +
               (1 + Axis|ID), data = df_range)
summary(xmdl)
```

With treatment-codes, time is the reference level. It looks like compared to time, quantity is more expressed along the y axis (TypeQ:Axisy), and verticality is more expressed along the y axis (TypeV:Axisy).

Get predictions:

```{r get_preds}
source('../scripts/predict.glmm.R')
all_types <- unique(df_range$Type)
all_axis <- unique(df_range$Axis)
newdata <- expand.grid(all_types, all_axis) %>%
  rename(Type = Var1, Axis = Var2) %>%
  arrange(Type)
predict.glmm(xmdl, newdata = newdata) %>%
  mutate(Range = round(Range))
```

The model predicts quantity to be much more y-expanded. The same goes for valence. For time and number, there's no big difference between x and y.

## Analysis of categorical classifications

Load in Greg's classifications:

```{r cat_loadin}
E4cat <- read_csv('../data/E4_cat.csv')
E4cat %>% print(n = 4, width = Inf)
```

As was done for E2 and E3, only those that used the axis consistently contribute to the "AxisChoice" measure. This is so that responses that don't obey any conceptual order are not counted.

```{r NA_for_no_axes}
E4cat[which(E4cat$ConsistentAxis == 'no'), ]$AxisChoice <- NA
```

## Analysis of single versus combined axis choice

Recode horizontal and vertical to "single axis", so that it can be contrasted with diagonal.

```{r single_versus_diagonal}
E4cat <- mutate(E4cat,
                DiagonalVsRest = ifelse(AxisChoice == 'horizontal' | AxisChoice == 'vertical', 'single', AxisChoice))
```

Tabulate single versus diagonal choices:

```{r table_of_single_vs_diagonal}
xtab <- table(E4cat$DiagonalVsRest)
xtab
```

Proportions:

```{r single_vs_diagonal_props}
round(prop.table(xtab), 2)
```

Perform a binomial test:

```{r single_vs_diagonal_binom}
binom.test(xtab)
```

## Consistent axis use

Let's look at consistent axis choice overall:

```{r consistent_axis_overall}
table(E4cat$ConsistentAxis)
round(prop.table(table(E4cat$ConsistentAxis)), 2)
```

Let's look at consistent axis choice:

```{r consistent_axis}
xtab <- with(E4cat,
             table(Condition, ConsistentAxis))
xtab
```

Let's make a table of proportions for this, with row-wise proportions (convert these to percentages):

```{r consistent_axis_props}
round(prop.table(xtab, 1), 2)
```

Let's perform a Chi-Square test of this:

```{r consistent_axis_chisq}
chisq.test(xtab)
```

Not significant.

Check Cramer's V:

```{r consistent_axis_cramer}
cramersV(xtab)
```

Weak.

## Analysis of round responses

Look at number of round versus number of axial responses. This column needs to be created first:

```{r round_versus_axial}
axials <- c('diagonal', 'horizontal', 'vertical')
E4cat$RoundVsAxial <- NA
E4cat <- mutate(E4cat,
                RoundVsAxial = ifelse(ChoiceDetailed %in% axials, 'axial', RoundVsAxial),
                RoundVsAxial = ifelse(ChoiceDetailed == 'round', 'round', RoundVsAxial))
```

Tabulate round vs.a xial:

```{r round_ax_table}
table(E4cat$RoundVsAxial)
```

Proportions:

```{r round_ax_props}
round(prop.table(table(E4cat$RoundVsAxial)), 2)
```

Binomial test:

```{r round_ax_binomtest}
binom.test(table(E4cat$RoundVsAxial))
```

Look at whether there was a consistent direction (clockwise/counterclockwise) for the round responses:

```{r round_consistent_tab}
xtab <- table(E4cat$ConsistentRoundDirection)
xtab
```

Proportions:

```{r round_consistent_prop}
round(prop.table(xtab), 2)
```

Binomial test:

```{r round_consistent_binom}
binom.test(xtab)
```

Not significant.

Look at clockwise versus counterclockwise overall:

```{r clockwise_counterclockwise_sum}
table(E4cat$RoundDirectionDetailed)
round(prop.table(table(E4cat$RoundDirectionDetailed)), 2)
```

And a binomial test of this:

```{r clockwise_counterclockwise_binom}
binom.test(table(E4cat$RoundDirectionDetailed))
```

Look at clockwise versus counterclockwise for the RoundDirectionDetailed column:

```{r clockwise_per_cond}
xtab <- with(E4cat, table(Condition,
                  RoundDirectionDetailed))
xtab
```

Row-wise proportions for this:

```{r clockwise_per_cond_props}
prop.table(xtab, 1)
```

And a test of this:

```{r clockwise_per_cond_chisq}
chisq.test(xtab)
```

## Axis choice

Let's create a table of this:

```{r axis_by_cat}
xtab <- with(E4cat,
             table(Condition, AxisChoice))
xtab
```

Let's look at the proportions of that (row-wise proportions).

```{r axis_proportions}
round(prop.table(xtab, 1), 2)
```

Let's perform a Chi-Square test of this:

```{r axis_choice_chisq}
E4_chisq <- chisq.test(xtab)
E4_chisq
```

Not significant.

```{r axis_choice_chisq_stdres}
E4_chisq$stdres
```

Check Cramer's V:

```{r axis_choice_cramer}
cramersV(xtab)
```

Weak.

## (Unplanned) Post-hoc analysis: 

We suspect that the diagonal responses (evenly spread across tasks and low numbers) may mess up the results in this case. We have not planned the following analysis before the data was in: What if we restrict the Chi-Square test analysis to horizontal and vertical responses?

```{r restrict_chisq}
xtab <- with(E4cat,
             table(Condition, AxisChoice))
xtab <- xtab[, -1]
chisq.test(xtab)
chisq.test(xtab)$stdres
cramersV(xtab)
```

## Entropy

Let's check the entropy across the three categories diagonal/horizontal/vertical.

```{r axis_entropy}
E4_tab <- table(E4cat$Condition, E4cat$AxisChoice)
entropies <- apply(E4_tab, 1, entropy)
entropies <- round(entropies, 2)
entropies
```

Looks like time and number are the most variable. Quantity is the least variable, closely followed by valence.

## Plot with categories and entropy

Plot data:

```{r plot, fig.width = 11, fig.height = 4}

# Create subsidiary tables for plotting and transpose tables for easy looping:
E4_prop <- prop.table(E4_tab, 1)
E4_percents <- t(apply(round(E4_prop * 100, 0),
	FUN = function(x) str_c(x, '%'), MARGIN = 1))
E4_stdres <- round(E4_chisq$stdres, 1)

# Plotting parameters:
xfac <- 0.1
yfac <- 4.5
yfac2 <- 1.6
yfac_bottom <- 2
mycols <- c('steelblue4', 'indianred4', 'goldenrod3')
mylabs <- c('Horizontal', 'Vertical', 'Diagonal')

# Make a nice publication-ready plot of this:
quartz('', 14, 4)
par(mai = c(1, 1.5, 0.5, 0.5))
emptyplot(xlim = c(0, 15), ylim = c(0, 50))
axis(side = 2, at = seq(0, 50, 10),
	font = 2, las = 2, cex.axis = 1.5, lwd = 2)
mtext(text = 'Count', side = 2, line = 3.8,
	font = 2, cex = 2)
axis(side = 1, at = c(2, 6, 10, 14) - 0.5,
	labels = c('Quantity', 'Number', 'Time', 'Valence'),
	font = 2, cex.axis = 1.5, line = 0.5, tick = FALSE)
axis(side = 1, at = 2 - 0.5,
	labels = bquote(italic('H')==.(entropies[2])),
	font = 2, cex.axis = 1.20, line = 1.9, tick = FALSE)
axis(side = 1, at = 6 - 0.5,
	labels = bquote(italic('H')==.(entropies[1])),
	font = 2, cex.axis = 1.2, line = 1.9, tick = FALSE)
axis(side = 1, at = 10 - 0.5,
	labels = bquote(italic('H')==.(entropies[3])),
	font = 2, cex.axis = 1.2, line = 1.9, tick = FALSE)
axis(side = 1, at = 14 - 0.5,
	labels = bquote(italic('H')==.(entropies[4])),
	font = 2, cex.axis = 1.2, line = 1.9, tick = FALSE)

# Quantity bars:
this_row <- row.names(E4_tab) == 'Q'
col_seq <- c(2, 3, 1)
for (i in 1:3) {
  mycol <- col_seq[i]
	rect(xleft = i - 1 + xfac, xright = i - xfac,
		ybottom = 0, ytop = E4_tab[this_row, mycol],
		col = mycols[i], border = NA)
	text(x = i - 0.5, y = E4_tab[this_row, mycol] + yfac,
		labels = E4_percents[this_row, mycol],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E4_stdres[this_row, mycol]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5, y = E4_tab[this_row, mycol] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.7)
	text(x = i - 0.5, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}

# Number bars:
this_row <- row.names(E4_tab) == 'N'
col_seq <- c(2, 3, 1)
xshift <- 4
for (i in 1:3) {
  mycol <- col_seq[i]
	rect(xleft = i - 1 + xfac + xshift,
	     xright = i - xfac + xshift,
		ybottom = 0, ytop = E4_tab[this_row, mycol],
		col = mycols[i], border = NA)
	text(x = i - 0.5 + xshift, y = E4_tab[this_row, mycol] + yfac,
		labels = E4_percents[this_row, mycol],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E4_stdres[this_row, mycol]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5 + xshift,
	     y = E4_tab[this_row, mycol] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.7)
	text(x = i - 0.5 + xshift, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}

# Time bars:
this_row <- row.names(E4_tab) == 'T'
col_seq <- c(2, 3, 1)
xshift <- 8
for (i in 1:3) {
  mycol <- col_seq[i]
	rect(xleft = i - 1 + xfac + xshift,
	     xright = i - xfac + xshift,
		ybottom = 0, ytop = E4_tab[this_row, mycol],
		col = mycols[i], border = NA)
	text(x = i - 0.5 + xshift, y = E4_tab[this_row, mycol] + yfac,
		labels = E4_percents[this_row, mycol],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E4_stdres[this_row, mycol]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5 + xshift,
	     y = E4_tab[this_row, mycol] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.7)
	text(x = i - 0.5 + xshift, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}

# Valence bars:
this_row <- row.names(E4_tab) == 'V'
col_seq <- c(2, 3, 1)
xshift <- 12
for (i in 1:3) {
  mycol <- col_seq[i]
	rect(xleft = i - 1 + xfac + xshift,
	     xright = i - xfac + xshift,
		ybottom = 0, ytop = E4_tab[this_row, mycol],
		col = mycols[i], border = NA)
	text(x = i - 0.5 + xshift, y = E4_tab[this_row, mycol] + yfac,
		labels = E4_percents[this_row, mycol],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E4_stdres[this_row, mycol]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5 + xshift,
	     y = E4_tab[this_row, mycol] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.7)
	text(x = i - 0.5 + xshift, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}

```

## Dominant direction

Let's look at dominant direction, for horizontal overall:

```{r dom_direct_horz}
table(E4cat$AxialDirectionHorizontal)
round(prop.table(table(E4cat$AxialDirectionHorizontal)), 2)
```

For horizontal by task:

```{r dom_direct_horz_task}
xtab <- with(E4cat,
     table(Condition, AxialDirectionHorizontal))
xtab
round(prop.table(xtab, 1), 2)
```

Entropy of that:

```{r dom_direct_horz_task_entr}
xtab <- with(E4cat,
     table(Condition, AxialDirectionHorizontal))
round(apply(xtab, 1, entropy), 2)
```

Horizontal entropy most variable for quantity and valence, least variable for numbers, then time! (Woohoo)

For vertical overall:

```{r dom_direct_vert}
table(E4cat$AxialDirectionVertical)
round(prop.table(table(E4cat$AxialDirectionVertical)), 2)
```

For vertical by task:

```{r dom_direct_vert_task}
xtab <- with(E4cat,
     table(Condition, AxialDirectionVertical))
xtab
round(prop.table(xtab, 1), 2)
```

Entropy of that:

```{r dom_direct_vert_task_entr}
xtab <- with(E4cat,
     table(Condition, AxialDirectionVertical))
round(apply(xtab, 1, entropy), 2)
```

The reverse from the above entropies!  Quantity least vertically variable, followed by valence, then number, then time (sweet!).

Let's look at detailed responses.

```{r}
table(E4cat$AxialDirectionDetailed)
```


## Analysis of interview data

Load in interview data:

```{r load_interviews}
E4qual <- read_csv('../data/E4_IT.csv')
```

- maths & numbers together "AllMaths"
- environment
- radial / bullseye
- clock
- timeline
- writing

For all the sections headed with "Interview:", the counts and proportions are pooled across all participants (counts/proportions of trials overall).

## Interview: Maths / numbers

Combine maths and numbers for allmaths. For the numbers task this does not need to be done because it's always about numbers anyway and this has been coded in the "NumbersNumber" column.

```{r combine_maths}
E4qual <- mutate(E4qual,
                 TimeAllMath = ifelse(TimeMaths == 'yes' | TimeNumber == 'yes', 'yes', 'no'),
                 QuantityAllMath = ifelse(QuantityMaths == 'yes' | QuantityNumber == 'yes', 'yes', 'no'),
                 ValenceAllMath = ifelse(ValenceMaths == 'yes' | ValenceNumber == 'yes', 'yes', 'no'))
```

Let's look at this:

```{r allmaths_tables}
# Time:

table(E4qual$TimeAllMath)
round(prop.table(table(E4qual$TimeAllMath)), 2)

# Valence:

table(E4qual$ValenceAllMath)
round(prop.table(table(E4qual$ValenceAllMath)), 2)

# Quantity:

table(E4qual$QuantityAllMath)
round(prop.table(table(E4qual$QuantityAllMath)), 2)

# Number:

table(E4qual$NumbersMaths)
round(prop.table(table(E4qual$NumbersMaths)), 2)
```

## Interview: Environment

Overall environment per condition:

```{r environment_table}
# Time:

table(E4qual$TimeEnvironment)
round(prop.table(table(E4qual$TimeEnvironment)), 2)

# Valence:

table(E4qual$ValenceEnvironment)
round(prop.table(table(E4qual$ValenceEnvironment)), 2)

# Quantity:

table(E4qual$QuantityEnvironment)
round(prop.table(table(E4qual$QuantityEnvironment)), 2)

# Number:

table(E4qual$NumbersEnvironment)
round(prop.table(table(E4qual$NumbersEnvironment)), 2)
```

## Interview: Timeline

Overall Timeline per condition:

```{r Timeline_tables}
# Time:

table(E4qual$TimeTimeline)
round(prop.table(table(E4qual$TimeTimeline)), 2)

# Valence:

table(E4qual$ValenceTimeline)
round(prop.table(table(E4qual$ValenceTimeline)), 2)

# Quantity:

table(E4qual$QuantityTimeline)
round(prop.table(table(E4qual$QuantityTimeline)), 2)

# Number:

table(E4qual$NumbersTimeline)
round(prop.table(table(E4qual$NumbersTimeline)), 2)
```

## Interview: Writing

Overall Writing per condition:

```{r Writing_tables}
# Time:

table(E4qual$TimeWriting)
round(prop.table(table(E4qual$TimeWriting)), 2)

# Valence:

table(E4qual$ValenceWriting)
round(prop.table(table(E4qual$ValenceWriting)), 2)

# Quantity:

table(E4qual$QuantityWriting)
round(prop.table(table(E4qual$QuantityWriting)), 2)

# Number:

table(E4qual$NumbersWriting)
round(prop.table(table(E4qual$NumbersWriting)), 2)
```

## Interview: Radial

Overall Radial per condition:

```{r radial_tables}
# Time:

table(E4qual$TimeRadial)
round(prop.table(table(E4qual$TimeRadial)), 2)

# Valence:

table(E4qual$ValenceRadial)
round(prop.table(table(E4qual$ValenceRadial)), 2)

# Quantity:

table(E4qual$QuantityRadial)
round(prop.table(table(E4qual$QuantityRadial)), 2)

# Number:

table(E4qual$NumbersRadial)
round(prop.table(table(E4qual$NumbersRadial)), 2)
```

## Interview: Clock

Overall clock per condition:

```{r clock_tables}
# Time:

table(E4qual$TimeClock)
round(prop.table(table(E4qual$TimeClock)), 2)

# Valence:

table(E4qual$ValenceClock)
round(prop.table(table(E4qual$ValenceClock)), 2)

# Quantity:

table(E4qual$QuantityClock)
round(prop.table(table(E4qual$QuantityClock)), 2)

# Number:

table(E4qual$NumbersClock)
round(prop.table(table(E4qual$NumbersClock)), 2)
```

## Interview: Bullseye

Overall Bullseye per condition:

```{r Bullseye_tables}
# Time:

table(E4qual$TimeBullseye)
round(prop.table(table(E4qual$TimeBullseye)), 2)

# Valence:

table(E4qual$ValenceBullseye)
round(prop.table(table(E4qual$ValenceBullseye)), 2)

# Quantity:

table(E4qual$QuantityBullseye)
round(prop.table(table(E4qual$QuantityBullseye)), 2)

# Number:

table(E4qual$NumbersBullseye)
round(prop.table(table(E4qual$NumbersBullseye)), 2)
```

## Relationship between interviews and axes

This part is exploratory. There are lots of associations between the interview data and the responses to look at. We are going to focus on results that stand out to us, or that are theoretically interesting.

Merge the two datasets:

```{r merge_interviews_plus_responses}
E4both <- left_join(E4cat, E4qual)
```

## Interview & response: Clock & round responses

Round vs axial, don't mind the fact that the table says QuantityClock, it's across all trials:

```{r clock_by_trial}
Q_clock <- with(filter(E4both, Condition == 'Q'),
     table(QuantityClock, RoundVsAxial))
Q_clock
N_clock <- with(filter(E4both, Condition == 'N'),
     table(NumbersClock, RoundVsAxial))
N_clock
T_clock <- with(filter(E4both, Condition == 'T'),
     table(TimeClock, RoundVsAxial))
T_clock
V_clock <- with(filter(E4both, Condition == 'V'),
     table(ValenceClock, RoundVsAxial))
V_clock
xtab <- Q_clock + N_clock + T_clock + V_clock
xtab
prop.table(xtab, 1)
```

Same for axis choice:

```{r clock_by_trial_axischoice}
Q_clock <- with(filter(E4both, Condition == 'Q'),
     table(QuantityClock, AxisChoice))
Q_clock
N_clock <- with(filter(E4both, Condition == 'N'),
     table(NumbersClock, AxisChoice))
N_clock
T_clock <- with(filter(E4both, Condition == 'T'),
     table(TimeClock, AxisChoice))
T_clock
V_clock <- with(filter(E4both, Condition == 'V'),
     table(ValenceClock, AxisChoice))
V_clock
xtab <- Q_clock + N_clock + T_clock + V_clock
xtab
prop.table(xtab, 1)
```

Of course, then it makes no sense to look at axis choice, because those who mentioned clocks for those trials responded roundly anyway.

Same for counter clockwise versus clockwise:

```{r clock_by_trial_ccw}
Q_clock <- with(filter(E4both, Condition == 'Q'),
     table(QuantityClock, RoundDirectionDetailed))
Q_clock
N_clock <- with(filter(E4both, Condition == 'N'),
     table(NumbersClock, RoundDirectionDetailed))
N_clock
T_clock <- with(filter(E4both, Condition == 'T'),
     table(TimeClock, RoundDirectionDetailed))
T_clock
V_clock <- with(filter(E4both, Condition == 'V'),
     table(ValenceClock, RoundDirectionDetailed))
V_clock
xtab <- Q_clock + N_clock + T_clock + V_clock
xtab
prop.table(xtab, 1)
```

## Interview & response: Vertical & axis & environment

```{r Environment_by_trial}
Q_Environment <- with(filter(E4both, Condition == 'Q'),
     table(QuantityEnvironment, RoundVsAxial))
Q_Environment
N_Environment <- with(filter(E4both, Condition == 'N'),
     table(NumbersEnvironment, RoundVsAxial))
N_Environment
T_Environment <- with(filter(E4both, Condition == 'T'),
     table(TimeEnvironment, RoundVsAxial))
T_Environment
V_Environment <- with(filter(E4both, Condition == 'V'),
     table(ValenceEnvironment, RoundVsAxial))
V_Environment
xtab <- Q_Environment + N_Environment + T_Environment + V_Environment
xtab
prop.table(xtab, 1)
```

This is for all!

Same for axis choice:

```{r Environment_by_trial_axischoice}
Q_Environment <- with(filter(E4both, Condition == 'Q'),
     table(QuantityEnvironment, AxisChoice))
N_Environment <- with(filter(E4both, Condition == 'N'),
     table(NumbersEnvironment, AxisChoice))
T_Environment <- with(filter(E4both, Condition == 'T'),
     table(TimeEnvironment, AxisChoice))
V_Environment <- with(filter(E4both, Condition == 'V'),
     table(ValenceEnvironment, AxisChoice))
xtab <- Q_Environment + N_Environment + T_Environment + V_Environment
xtab
prop.table(xtab, 1)
```

This is for all!

## Interview & response: Timeline & horizontal

Time line mentioning and horizontal responses.

```{r Timeline_by_trial}
Q_Timeline <- with(filter(E4both, Condition == 'Q'),
     table(QuantityTimeline, RoundVsAxial))
Q_Timeline
N_Timeline <- with(filter(E4both, Condition == 'N'),
     table(NumbersTimeline, RoundVsAxial))
N_Timeline
T_Timeline <- with(filter(E4both, Condition == 'T'),
     table(TimeTimeline, RoundVsAxial))
T_Timeline
V_Timeline <- with(filter(E4both, Condition == 'V'),
     table(ValenceTimeline, RoundVsAxial))
V_Timeline
xtab <- Q_Timeline + N_Timeline + T_Timeline[1, ] + V_Timeline
xtab <- rbind(xtab, T_Timeline[2, ])
row.names(xtab) <- c('no', 'yes')
xtab
prop.table(xtab, 1)
```

Same for axis choice:

```{r Timeline_by_trial_axischoice}
Q_Timeline <- with(filter(E4both, Condition == 'Q'),
     table(QuantityTimeline, AxisChoice))
Q_Timeline
N_Timeline <- with(filter(E4both, Condition == 'N'),
     table(NumbersTimeline, AxisChoice))
N_Timeline
T_Timeline <- with(filter(E4both, Condition == 'T'),
     table(TimeTimeline, AxisChoice))
T_Timeline
V_Timeline <- with(filter(E4both, Condition == 'V'),
     table(ValenceTimeline, AxisChoice))
V_Timeline
xtab <- Q_Timeline + N_Timeline + T_Timeline[1, ] + V_Timeline
xtab <- rbind(xtab, T_Timeline[2, ])
row.names(xtab) <- c('no', 'yes')
xtab
prop.table(xtab, 1)
```

Almost all were horizontal for those who mentioned timelines, and that was in the time condition.



