---
title: "Preprocessing Experiment 1 data"
author: "Bodo Winter & Greg Woodin"
date: "03/10/2018 - 10/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis of Experiment 1

This is the analysis of Experiment 1. Start loading packages, function file and data:

```{r libraries, message = FALSE}

library(tidyverse)	# for data processing
library(stringr)	# for data processing
library(lme4)	# for mixed models
library(afex)	# for mixed models
library(MuMIn)	# for mixed models
library(lsr)    # for calculating Cramer's V 

source('../scripts/functions.R')

E1 <- read_csv("../data/E1.csv")    
E1 %>% print(n = 6, width = Inf)

E1l <- read_csv('../data/E1_long.csv')    # long
E1l %>% print(n = 6, width = Inf)

```

Label horizontal and vertical directions of diagonal responses:

```{r diag_dir}

# Diagonal1: down-left to up-right
# Diagonal1Reverse: up-right to down-left
# Diagonal2: up-left to down-right
# Diagonal2Reverse: down-right to up-left

# Horizontal direction
E1l$HorizontalDiag <- E1l$Horizontal
E1l[E1l$ResponseDirection %in% c('Diagonal1', 'Diagonal2'), ]$HorizontalDiag <- 'left-to-right'
E1l[E1l$ResponseDirection %in% c('Diagonal1Reverse', 'Diagonal2Reverse'), ]$HorizontalDiag <- 'right-to-left'

# Vertical direction:
E1l$VerticalDiag <- E1l$Vertical
E1l[E1l$ResponseDirection %in% c('Diagonal1Reverse', 'Diagonal2'), ]$VerticalDiag <- 'down-to-up'
E1l[E1l$ResponseDirection %in% c('Diagonal2Reverse', 'Diagonal2'), ]$VerticalDiag <- 'up-to-down'
```

# Dominant Orientation

Find numbers and percentages of people who responded horizontally, vertically or diagonally for quantity, time and valence tasks:

```{r axis_choice}

# Re-order categorical variables:
E1l <- mutate(E1l,
	Condition = factor(Condition, levels = c('Quantity', 'Time', 'Valence')),
	AxisChoice = factor(ResponseAxis,	levels = c('Horizontal', 'Vertical', 'Diagonal')))

# Descriptive stats:
E1l %>% group_by(Condition, AxisChoice) %>% count() %>%
	mutate(Percentage = round(n / 50, 2) * 100)

```

Perform a Chi-square test on this and get Pearson's standardised residuals and Cramer's V:

```{r inferential}

E1_xtab <- with(E1l, table(Condition, AxisChoice))
print(E1_chisq <- chisq.test(E1_xtab))	# violates independence
E1_chisq$stdres	# violates independence
cramersV(E1_xtab)	# small = 0.1, medium = 0.3, large = 0.8

```

Run loop with random sample of data points from unique participants 1000 times:

```{r for_loop}

nsim <- 1000
xchisq <- numeric(nsim)
cols <- c('QuantityAxis', 'TimeAxis', 'ValenceAxis')

alltabs <- vector('list', length = nsim)

set.seed(42)
for (i in 1:nsim) {
  
	# Assign empty vectors with names of columns:
	assign(cols[1], vector(mode = 'numeric', length = 0))
	assign(cols[2], vector(mode = 'numeric', length = 0))
	assign(cols[3], vector(mode = 'numeric', length = 0))
	
	# Loop through participants and select one data point each:
	for (j in 1:50) {
		this_task <- sample(cols, 1)
		assign(this_task,
			c(get(this_task),
				pull(E1[j, ], this_task)))
		}

	# Tabulate this:
	QuantityAxis <- as_tibble(table(QuantityAxis))
	TimeAxis <- as_tibble(table(TimeAxis))
	ValenceAxis <- as_tibble(table(ValenceAxis))

	# Join the table:
	xdata <- full_join(ValenceAxis, QuantityAxis, by = c('ValenceAxis' = 'QuantityAxis'))
	xdata <- full_join(xdata, TimeAxis, by = c('ValenceAxis' = 'TimeAxis'))
	
	# Extract matrix:
	xdata <- as.matrix(xdata[, 2:4])
	if (any(is.na(xdata))) xdata[is.na(xdata)] <- 0
	alltabs[[i]] <- xdata

	# Save the Chisquare value:
	suppressWarnings(this_chisq <- chisq.test(xdata))
	xchisq[i] <- this_chisq$statistic
	
	# Notify:
	if (i %% 100 == 0) cat(paste0(i, '\n'))
	}

# Significance threshold for df = 4 and a = 0.05:
chisq_crit <- qchisq(0.05, 4, lower.tail = FALSE)
sum(xchisq < chisq_crit)
sum(1 - pchisq(xchisq, df = 4) > 0.05)	# check
mean(xchisq)
1 - pchisq(mean(xchisq), df = 4)	# significance of average Chi-Square value

```

To double-check, perform a logistic mixed model of horizontal versus vertical:

```{r logistic}

E1log <- filter(E1l, AxisChoice != 'Diagonal') %>%
	mutate(AxisChoice = droplevels(AxisChoice))

mymdl <- glmer(AxisChoice ~ Condition + (1|Subject),
	data = E1log, family = 'binomial')

summary(mymdl)

mixed(AxisChoice ~ Condition + (1|Subject),
	data = E1log, family = 'binomial', method = 'LRT')

```

Compare single-axis versus diagonal responses:

```{r continuity}

E1_diag_vs_no <- matrix(c(E1_xtab[, 'Horizontal'] + E1_xtab[, 'Vertical'],
	E1_xtab[, 'Diagonal']), nrow = 3, byrow = FALSE)

colSums(E1_diag_vs_no)

prop.table(colSums(E1_diag_vs_no))

binom.test(colSums(E1_diag_vs_no))

```

Calculate Shannon entropy:

```{r entropy}

entropies <- round(apply(E1_xtab, MARGIN = 1, FUN = entropy), 2)

```

Create plot of results:

```{r plot}

# Create subsidiary tables for plotting and transpose tables for easy looping:
E1_prop <- prop.table(E1_xtab, 1)
E1_percents <- t(apply(round(E1_prop * 100, 0),
	FUN = function(x) str_c(x, '%'), MARGIN = 1))
E1_stdres <- round(E1_chisq$stdres, 1)

# Plotting parameters:
xfac <- 0.1
yfac <- 4.5
yfac2 <- 1.6
yfac_bottom <- 2
mycols <- c('steelblue4', 'indianred4', 'goldenrod3')
mylabs <- c('Horizontal', 'Vertical', 'Diagonal')

# Make plot:
quartz('', 11, 4)
par(mai = c(1, 1.5, 0.5, 0.5))
emptyplot(xlim = c(0, 11), ylim = c(0, 40))
axis(side = 2, at = seq(0, 40, 10),
	font = 2, las = 2, cex.axis = 1.5, lwd = 2)
mtext(text = 'Count', side = 2, line = 3.8,
	font = 2, cex = 2)
axis(side = 1, at = c(2, 6, 10) - 0.5,
	labels = c('Quantity', 'Time', 'Valence'),
	font = 2, cex.axis = 1.5, line = 0.5, tick = FALSE)
axis(side = 1, at = 2 - 0.5,
	labels = bquote(italic('H')==.(entropies[2])),
	font = 2, cex.axis = 1.20, line = 1.9, tick = FALSE)
axis(side = 1, at = 6 - 0.5,
	labels = bquote(italic('H')==.(entropies[1])),
	font = 2, cex.axis = 1.2, line = 1.9, tick = FALSE)
axis(side = 1, at = 10 - 0.5,
	labels = bquote(italic('H')==.(entropies[3])),
	font = 2, cex.axis = 1.2, line = 1.9, tick = FALSE)

# Quantity bars:
for (i in 1:3) {
	rect(xleft = i - 1 + xfac, xright = i - xfac,
		ybottom = 0, ytop = E1_xtab[1, i],
		col = mycols[i], border = NA)
	text(x = i - 0.5, y = E1_xtab[1, i] + yfac,
		labels = E1_percents[1, i],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E1_stdres[2, i]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5, y = E1_xtab[1, i] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.9)
	text(x = i - 0.5, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}

# Time bars:
for (i in 1:3) {
	rect(xleft = i - 1 + xfac + 4, xright = i - xfac + 4,
		ybottom = 0, ytop = E1_xtab[2, i],
		col = mycols[i], border = NA)
	text(x = i - 0.5 + 4, y = E1_xtab[2, i] + yfac,
		labels = E1_percents[2, i],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E1_stdres[2, i]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5 + 4, y = E1_xtab[2, i] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.9)
	text(x = i - 0.5 + 4, y = 0 - yfac_bottom,
		labels = mylabs[i],adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}

# Valence bars:
for (i in 1:3) {
	rect(xleft = i - 1 + xfac + 8, xright = i - xfac + 8,
		ybottom = 0, ytop = E1_xtab[3, i],
		col = mycols[i], border = NA)
	text(x = i - 0.5 + 8, y = E1_xtab[3, i] + yfac,
		labels = E1_percents[3, i],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- E1_stdres[3, i]
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5 + 8, y = E1_xtab[3, i] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.9)
	text(x = i - 0.5 + 8, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.9, xpd = NA)
}
```

## Dominant Direction

Find out how many participants responded from left-to-right, up-to-down etc. 
```{r direction}

# Horizontal (Table 1):

(E1_hor_tab <- with(E1l, table(Condition, Horizontal)))
(E1_hor_props <- prop.table(E1_hor_tab, 1))

## Entropies per task (Table 1):

E1_horizontal_entropies <- apply(E1_hor_tab, MARGIN = 1,
	FUN = entropy)

# Vertical (Table 1):

(E1_ver_tab <- with(E1l, table(Condition, Vertical)))
(E1_ver_props <- prop.table(E1_ver_tab, 1))

## Entropies per task (Table 1):

E1_vertical_entropies <- apply(E1_ver_tab, MARGIN = 1,
	FUN = entropy)

## Diagonal (Table 2):

E1l_diag <- filter(E1l, ResponseAxis == 'Diagonal')
print(E1_diagonal_horz <- with(E1l_diag, table(Condition, HorizontalDiag)))
print(E1_diagonal_vert <- with(E1l_diag, table(Condition, VerticalDiag)))
prop.table(E1_diagonal_horz, 1)
prop.table(E1_diagonal_vert, 1)

## Entropies per axis per task:

print(E1_horz_entropies <- apply(E1_diagonal_horz, MARGIN = 1,
	FUN = entropy))
print(E1_vert_entropies <- apply(E1_diagonal_vert, MARGIN = 1,
	FUN = entropy))

```