---
title: "Preprocessing Experiment 3 Data"
author: "Bodo Winter & Greg Woodin"
date: "10/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Categorical analysis of Experiment 3

This is the categorical analysis of Experiment 3. Start loading packages, function file and data:

```{r libraries, message = FALSE}

library(tidyverse)	# for data processing
library(stringr)	# for data processing
library(lme4)	# for mixed models
library(afex)	# for mixed models
library(MuMIn)	# for mixed models
library(lsr)    # for calculating Cramer's V 

source('../scripts/functions.R')

E3 <- read_csv('../data/E3_cat.csv')
E3 %>% print(n = 6, width = Inf)

```

Recode Axis as ‘Other / no pattern’ if Consistency == no:

```{r recode}

E3[E3$Direction == 'n/a', ]$Representation <- 'Other / no pattern'

```

## Axis Consistency

Find out how many participants used an axis to structure their response:

```{r axis}

E3_tab <- table(E3$Representation)
print(cons <- sum(E3_tab[names(E3_tab) != 'Other / no pattern']))   # consistent axis
print(incons <- sum(E3_tab[names(E3_tab) == 'Other / no pattern']))   # inconsistent axis
prop.table(c(cons, incons))

```

## Dominant Orientation

Find out what axis participants chose for each task:

```{r orientation}

# Descriptive stats:
(E3_tab <- table(E3$Representation)[c('Horizontal', 'Vertical', 'Diagonal')])
E3_props <- prop.table(E3_tab)
(E3_percents <- str_c(round(E3_props * 100, 0), '%'))

# Perform a Chi-square test on this:
chisq.test(E3_tab)
chisq.test(E3_tab)$stdres
cramersV(E3_tab)	# small = 0.1, medium = 0.3, large = 0.8

```

Compare E3 results (exact numerals) with E1 and E2 (quantities):

```{r compare}

# Load in E1 data:
E1 <- read_csv("../data/E1.csv")

# Load in E2 data:
E2 <- read_csv("../data/E2cat_long.csv")

# Preliminary data wrangling to match E2_cat_analysis.Rmd:
E2[is.na(E2$DirectionDetailed), ]$AxisChoice <- 'other'
E2[is.na(E2$DirectionDetailed), ]$AxisChoiceDetailed <- 'other / no pattern'
E2[is.na(E2$AxisChoice), ]$AxisChoice <- 'other'

# Merge with E1 and E2 axis orientations:
E1_num_tab <- table(E1$QuantityAxis)[c('Horizontal', 'Vertical', 'Diagonal')]
E2_num_tab <- table(filter(E2, Condition == 'Quantity')$AxisChoice)[c('horizontal', 'vertical', 'diagonal')]
names(E2_num_tab) <- c('Horizontal', 'Vertical', 'Diagonal')

# Chi-Square tests:
print(E1_vs_E3_chisq <- chisq.test(bind_rows(E3_tab, E1_num_tab)))
print(E2_vs_E3_chisq <- chisq.test(bind_rows(E3_tab, E2_num_tab)))

# Look at standardized residuals:
round(E1_vs_E3_chisq$stdres, 1)
round(E2_vs_E3_chisq$stdres, 1)

# Get entropies:
entropy(E3_tab)
entropy(E1_num_tab)
entropy(E2_num_tab)

```

Make plot of this data:

```{r plot}

# Plotting parameters:
xfac <- 0.1
yfac <- 4.5
yfac2 <- 1.6
yfac_bottom <- 2
mycols <- c('steelblue4', 'indianred4', 'goldenrod3')
mylabs <- c('Horizontal', 'Vertical', 'Diagonal')

quartz('', 6, 4)
par(mai = c(1, 1.5, 0.5, 0.5))
emptyplot(xlim = c(0, 3), ylim = c(0, 40))
axis(side = 2, at = seq(0, 40, 10),
	font = 2, las = 2, cex.axis = 1.5, lwd = 2)
mtext(text = 'Count', side = 2, line = 3.8,
	font = 2, cex = 2)
axis(side = 1, at = c(2) - 0.5,
	labels = c('Quantity, exact'),
	font = 2, cex.axis = 1.5, line = 0.5, tick = FALSE)
axis(side = 1, at = 2 - 0.5,
	labels = bquote(italic('H')==.(round(entropy(E3_tab), 2))),
	font = 2, cex.axis = 1.20, line = 1.9, tick = FALSE)

# Quantity bars:
for (i in 1:3) {
	rect(xleft = i - 1 + xfac, xright = i - xfac,
		ybottom = 0, ytop = E3_tab[i],
		col = mycols[i], border = NA)
	text(x = i - 0.5, y = E3_tab[i] + yfac,
		labels = E3_percents[i],
		font = 2)
	
	# Fix stdres values for presentation:
	this_stdres <- round(chisq.test(E3_tab)$stdres[i], 1)
	stdres_display <- this_stdres
	if (this_stdres %% 1 == 0) {
		stdres_display <- str_c(stdres_display, '.0')
	}
	if (this_stdres > 0) {
		stdres_display <- str_c('+', as.character(stdres_display))
	}
	text(x = i - 0.5, y = E3_tab[i] + yfac2,
		labels = bquote(italic('r')==.(stdres_display)),
		font = 2, cex = 0.9)
	text(x = i - 0.5, y = 0 - yfac_bottom,
		labels = mylabs[i], adj = c(0.5, 0.5),
		font = 2, cex = 0.8, xpd = NA)
	}

```

Look at whether participants who took part in both E1 and E3 switched their choice of axis from E1 to E3:

```{r compare_E1}

# Merge E1 and E3 (note: subjects 31A - 50A correspond to subjects 31-50 in E1)
E3_E1match <- filter(E3, Subject %in% str_c(31:50, 'A')) %>%
	mutate(Subject = str_extract(Subject, '[0-9]+'),
		Subject = as.integer(Subject)) %>%
	left_join(E1, by = c('Subject' = 'Subject'))
with(E3_E1match, table(QuantityAxis, Representation))

# Count number of 'switchers':
3 + 5 + 2 + 1 + 3 + 2

# Count total number of participants who took part in E1 and E3:
sum(with(E3_E1match, table(QuantityAxis, Representation)))

# Count total number of responses for each type of response overall across E1 and E3:
colSums(with(E3_E1match, table(QuantityAxis, Representation)))

# Descriptive stats:
switchers <- c(0, 1, 6, 9)	# vertical, diagonal, horizontal, other/no-pattern
switchers / sum(switchers)	# percentages

# Perform a Chi-square test on this:
chisq.test(switchers)

```

Look at whether participants who took part in both E2 and E3 switched their choice of axis from E2 to E3:

```{r compare_E2}

# Merge E1 and E3 (note: subjects 41B - 60B correspond to subjects 41 - 60 in E2))
E3_E2match <- filter(E3, Subject %in% str_c(41:60, 'B')) %>%
	mutate(Subject = str_extract(Subject, '[0-9]+'),
		Subject = as.integer(Subject)) %>%
	left_join(filter(E2, Condition == 'Quantity'), by = c('Subject' = 'Subject'))
with(E3_E2match, table(AxisChoice, Representation))

# Count number of 'switchers':
1 + 1 + 4 + 2 + 3 + 1

# Of those subjects that switched, find out what axis they switched to:
mytab <- with(E3_E2match, table(AxisChoice, Representation))
switchers <- mytab[1, ] + mytab[3, ] + mytab[4, ]
switchers[1] <- switchers[1] + 1	# the subject who switched from 'horizontal' to 'diagonal'
switchers[3] <- switchers[3] - 3	# the three subjects who stayed 'other'
switchers[4] <- switchers[4] - 1	# the subject who stayed 'vertical'
switchers
prop.table(switchers)

# Perform a Chi-square test on this:
chisq.test(switchers)

```
