---
title: "Preprocessing Experiment 4 data"
author: "Bodo Winter & Greg Woodin"
date: "10/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## E4 image creation

To make the analysis of E4 maximally comparable to E1-E3, we hand-coded images according to categorical axis labels ("horizontal", "vertical" etc.)

This Markdown script creates the image files on which the hand-coding was based.

Start loading packages, function file and data:

```{r libraries, message = FALSE}
library(tidyverse)
library(stringr)

source('../scripts/functions.R')

df <- read_csv("../data/E4_processed.csv")
df %>% print(n = 6, width = Inf)
```

Create unique subject / task combination (one circle each):

```{r unique_sub_task}
df <- mutate(df,
             Task = str_c(ID, '_', Type))
all_tasks <- unique(df$Task)
```

Create plots and save as pngs into image folder:

```{r image_create}
file_path <- '../image_coding/'

for (i in seq_along(all_tasks)){
  id <- all_tasks[i]
	df_sub <- filter(df, Task == id)
	df_x <- filter(df_sub, Axis == 'x')
	df_y <- filter(df_sub, Axis == 'y')
	png(filename = str_c(file_path, id, '.png'),
	    width = 500, height = 500)
	emptyplot(xlim = c(0, 800), ylim = c(0, 800))
	text(x = df_x$Pixel, y = df_y$Pixel,
	     labels = df_x$Resp, font = 2, cex = 2)
	dev.off()
	}
```

## Create table for coding image responses

Create table for coding:

```{r create_qual_table}
coding_table <- tibble(all_tasks) %>%
  separate(all_tasks, into = c('ID', 'Type'))
```

Initiate some columns:

```{r write_coding_table}
coding_table$ConsistentAxis <- NA
coding_table$Orientation <- NA
coding_table$HorizontalDirection <- NA
coding_table$VerticalDirection <- NA

# write_csv(coding_table,
          #'../data/coding_table.csv')
```

## Coding table for qualitative interview repsonses

Create table for coding interview responses:

```{r qual_create}
qual_df <- df[!duplicated(df$ID), ] %>%
  select(ID, Exp1:Exp4)
#write_csv(qual_df, #'../data/quantitative_data/qual_responses.csv')
```








